\documentclass[aspectratio=169]{beamer}

\setbeamertemplate{headline}

% generic packages

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% about the presentation
\title{Constrained RESTful Application Languager (CoRAL)}
\hypersetup{pdftitle={Constrained RESTful Application Languager (CoRAL)}}
\subtitle{Interim status update}
\date{2021-10-13}

\hypersetup{colorlinks}

% get page numbers without author and institute, especially given the institute hack later to get sizes consistent

% thanks Andrea, from https://tex.stackexchange.com/questions/179304/redefining-infolines-in-beamer
\defbeamertemplate*{footline}{infolines}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
    \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
    \insertframenumber{} / \inserttotalframenumber\hspace*{2ex} 
  \end{beamercolorbox}}%
  \vskip0pt%
}

% and, given that it has no deep structure and navigation can't be used through meetecho anyway, remove other clutter from there

\beamertemplatenavigationsymbolsempty

% attach self

\usepackage{embedfile}
\embedfile{\jobname.tex}
\embedfile{Makefile}

\begin{document}

\frame{\titlepage}

\begin{frame}{Recap from last status update}\Large
  \begin{itemize}
    \item Information model merged
      \begin{itemize}\large
        \item Basic model contains statements (graph; ``</x> core:ct 40'')
        \item Structured model shapes them (sequence of statements, nesting)
        \item Forms and embedded payloads are built on top of the model
      \end{itemize}
    \bigskip
    \item How to handle literals?
      \begin{itemize}\large
        \item[$-$] Entity with arbitrary outgoing edges

          </g> core:label "Gift" (instance 1).\\
          "Gift" (instance 1) xml:lang "en".
''
        \item[$+$] Value-with-properties

          </g> core:label "Gift"@en.
      \end{itemize}
      \footnotesize (Not that it'd matter for the serialization\ldots)
  \end{itemize}
\end{frame}

\begin{frame}{New in the editor's copy since last time}\Large
  \begin{itemize}
    \item Packed CBOR
    \item CBOR diagnostic notation (with EDN) replaces text format
    \item Mappings with Link Format and RDF

      \bigskip

      \em{``Applications that use links with the attribute semantics common in the CoRE ecosystem (typically used with RFC6690 Link Format) can use this conversion. ''}
  \end{itemize}
\end{frame}

\begin{frame}[fragile]{Link Format mapping}\small
  \begin{verbatim}
</sensors>;ct=40;title="Sensor Index",
</sensors/temp>;rt="temperature-c";if="sensor tag:example.com:mysensor",
<http://www.example.com/sensors/t123>;anchor="/sensors/temp";rel="describedby"
  \end{verbatim}

  \begin{verbatim}
[
  [2, simple(10) / rel:hosts /, cri'/sensors', [
    [2, 6(2) / core:ct /, 40],
    [2, simple(15) / core:title /, 'Sensor Index']
  ]],
  [2, simple(10) / rel:hosts /, cri'/sensors/temp', [
    [2, 6(1) / core:if /, 6(200) / cri'http:...temperature-c' /],
    [2, 6(1) / core:if /, cri'tag:example.com:mysensor' ],
    [2, 6(-2) / core:rt /, 6(250) / cri'http:...sensor' /],
    [2, simple(12) / rel:describedby /, cri'http://www.example.com/sensors/t123'],
  ]]
]
  \end{verbatim}
\end{frame}

\begin{frame}{Current issues}\Large
  \begin{itemize}
    \item Reasons left for deterministic encoding? \href{https://github.com/core-wg/coral/issues/5}{\#5}
    \item Lock in the ``property'' model of literals? \href{https://github.com/core-wg/coral/issues/10}{\#10}
    \item Can we do without circular visitation? \href{https://github.com/core-wg/coral/issues/9}{\#9}

      (And if so, do we want to use this for a flatter file format?)
    \item Open or Closed World? \href{https://github.com/core-wg/coral/issues/3}{\#3}

      (Not that we'd have to decide -- but allowing both, guide people to be open-world compatible.)
  \end{itemize}
\end{frame}

\end{document}
