\documentclass[aspectratio=169,colorlinks]{beamer}
\usetheme{Boadilla} % plainest one with slide number footer

% generic packages

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{ulem}

% about the presentation
\title[CoRAL]{The Constrained RESTful Application Language (CoRAL)}
\hypersetup{pdftitle={The Constrained RESTful Application Language (CoRAL)}}
\subtitle{\texttt{draft-ietf-core-coral-05}}
\author{\textit{Christian~Amsüss}, Thomas~Fossati}
\date{2022-07-26, IETF 114}

% used commands

\usepackage{verbatim}

\definecolor{darkgreen}{rgb}{0, 0.56, 0}

% attach self

\usepackage{embedfile}
\embedfile{Makefile}
\embedfile{\jobname.tex}

\begin{document}

\frame{\titlepage}

\begin{frame}{CoRAL}\Large
	A data model and language for talking about resources and interactions with them,
	suitable for constrained devices
\end{frame}

\begin{frame}{CoRAL: Properties relevant for today}\Large
	\begin{itemize}
		\item Information model is similar to RDF

		\item CBOR based representation of URIs and structure

	\end{itemize}

	\vfill

	``{\color{red}My temperature resource} {\color{darkgreen}supports} {\color{blue}the Series Transfer Pattern}.''

	\texttt{{\color{red}</temp>} {\color{darkgreen}core:if} {\color{blue}<tag:example.com,2020,t2trg-stp>}.}

	\vfill

	\normalsize \ldots plus some features not covered today, such as navigation through forms, localization, and convertability with suitable Link Format documents or RDF.
\end{frame}

\begin{frame}{Recent model simplification: Literals}\Large
	Literals are terminal nodes in the graph.

	Any properties literals might have are expressed through CBOR tags.

	\bigskip

	\texttt{problem-details} did the hard work here.
\end{frame}

\begin{frame}{Ongoing work: Compact format based on \texttt{cbor-packed}}\Large
	\ttfamily

	{\color{darkgreen}core:rt} {\color{blue}pubsub:topic}, \\
	{\color{blue}pubsub:has-published-item} true, \\
	{\color{blue}pubsub:created} dt'2019-07-08T15:35:00+0200', \\
	{\color{blue}pubsub:last-modified} dt'2019-07-08T15:35:00+0200', \\

	{\color{blue}pubsub:topic-data} [ = </ps/data/1234>, \\
	\qquad {\color{darkgreen}core:title}               "My Office Room Temperature", \\
	\qquad {\color{darkgreen}core:rt}                  {\color{blue}oic:r.temperature}, \\
	\qquad {\color{red}our:building}            18, \\
	\qquad {\color{red}our:floor}               1, \\
	\qquad {\color{darkgreen}core:unit} {\color{magenta}unit:Cel}, \\
        ]

\end{frame}

\begin{frame}{Ongoing work: Compact format based on \texttt{cbor-packed}}\Large

	\begin{itemize}
		\item Some table entries initialized through media type.
		
			\texttt{\color{darkgreen}core:title} used compressed as
			\texttt{[2, {\color{darkgreen}6(14)}, "My Office "\ldots]}

		\item Registered ranges can be loaded without referencing dictionaries by any long identifiers

			\texttt{\color{blue}pubsub:*} pushed into tables through \texttt{TBD({\color{darkgreen}6(16)}, [10, 0], \ldots)}

		\item Custom terms are loaded by referencing URIs

			\texttt{\color{red}our:building} pushed into tables through \texttt{TBD(cri"https://our.example.com/tab", [3, 3], \ldots)}

		\item CRI CURIEs? \texttt{\color{magenta}unit:Cel}
	\end{itemize}

	\bigskip

	\footnotesize{Also join CBOR on Thursday for discussion of \texttt{cbor-packed}!}
\end{frame}

\begin{frame}{Ongoing work: Security model}\Large
	Use existing security models, but tell how to apply them.

	The CoRAL document should provide\ldots

	\begin{itemize}
		\item to application authors:

			Guidance on expressing their security requirements.

		\item to CoRAL agents:

			Rules for evaluating these security requirements against the authorizations conveyed in CoRAL documents.
	\end{itemize}
\end{frame}

\begin{frame}{Open areas and next steps}\Large
	\begin{itemize}
		\item Binary serialization -- needs more real-world examples, especially of forms.
		\item Mapping to \texttt{problem-details} -- now that that is done.
		\item Queries, patches, provenance -- likely not in initial version.
	\end{itemize}
\end{frame}

\begin{frame}{Thanks}\Large
	Comments?

	\bigskip

	Questions?
\end{frame}

\end{document}
